---
output: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# s7x - S7 extensions

[`{S7}`](https://rconsortium.github.io/S7/) utility extensions for scalar and enum-like properties.

<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of s7x like so:

``` r
pak::pak("josiahparry/s7x")
```

## Enums

S7 has no built-in enum type: a property can require a `class_character`, but nothing stops it holding any string at all. `new_enum_class()` fixes that by minting an S7 class scoped to a fixed set of variants, as described in [Enums in R](https://josiah.rs/posts/enums-in-r/).

```{r}
library(s7x)

GridShape <- new_enum_class("GridShape", c("Square", "Hexagon"))

GridShape("Square")
try(GridShape("Triangle"))
```

Use `property_enum()` to let another class hold an instance of one or more enum classes:

```{r}
Direction <- new_enum_class("Direction", c("North", "South", "East", "West"))

Board <- S7::new_class(
  "Board",
  properties = list(orientation = property_enum(GridShape, Direction))
)

Board(GridShape("Hexagon"))@orientation
Board(Direction("North"))@orientation
```
