---
output: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# s7x - S7 extensions

`{s7x}` provides utility extensions to the [`{S7}`](https://rconsortium.github.io/S7/) type system.

It fills the void of features I've long wanted in S7 (and R) to help make R packages more type safe(ish) with less boilerplate.

<!-- badges: start -->
<!-- badges: end -->

Notably s7x provides:

- an extensible `Enum` class for speficying enumerations
- scalar properties
- range propeties (discrete and continuous)
- property unions and intersections

See [Enums in R: towards type safe R](https://josiah.rs/posts/enums-in-r/) for the motivation behind this package.

## Installation

You can install the development version of s7x like so:

``` r
pak::pak("josiahparry/s7x")
```

:::{.callout-note}
`s7x` is built on the development version of `S7`. Install it with `pak::pak("RConsortium/S7")`.
:::

## Enum(eration)s

In R, we use enumerations all the time, though in formally. For example, `stats::cor()`'s argument `method = c("pearson", "kendall", "spearman")` is an enumeration in that `method` can be only one of three possible values. In R, enums are typically strings and validated via `arg.match()` or the equivalent `rlang::arg_match()`.

In `{s7x}`, enums are formalized through the `s7x::Enum` class.


```{r}
library(s7x)

# create a new enum
CorMethod <- new_enum("CorMethod", c("pearson", "kendall", "spearman"))

# instantiate the enum
x <- CorMethod("pearson")
x
```

Note that all `s7x::Enum`s can be cast as character vectors.

```{r}
as.character(x)
```

Thus, we can use the `Enum` to enforce variants, but when we need the underlying value we can `as.character()` or extract it's value via `x@value`.

## Scalar properties

A longtime [wish list item](https://github.com/RConsortium/S7/issues/554) of mine is **scalar** properties.
A scalar in R is a **length one** vector. These are useful for arguments such as `n_components = 5`—where it wouldn't make sense for the value to be `c(5, 1)`, for example.

S7 has built-in classes for the vector types in R (double, integer, character, list) but not for their scalar variants.

`s7x` introduces the `property_scalar()` function which lets you create **scalar** variants.

For example:

```{r, message=FALSE}
library(S7)
NComponents := new_class(properties = list(n = property_scalar(class_integer)))

n_comps <- NComponents(5L)
n_comps
```

Providing a non-length 1 value creates an error:

```{r, error = TRUE}
NComponents(c(5L, 1L))
```
